REVISITING SEMI-CONTINUOUS HIDDEN MARKOV MODELS

### 2011-09-28 misc/papers/icassp12_tied/icassp12.tex
Further edits to paper.
git-svn-id: https://svn.code.sf.net/p/kaldi/code/sandbox/discrim@535 5e6a8d80-dfce-4ca6-a32a-6e07a63d50c8

\subsection{Inter-Iteration Smoothing}
Another typical problem that arises when training semi-continuous models is
that the weights tend to converge to a poor local optimum over the iterations. 
Our intuition is that the weights tend to overfit to the Gaussian parameters
in such a way that the model quickly converges with the
GMM parameters very close to the initialization point.
%
To try to counteract this effect, we smooth the newly estimated parameters 
$\Theta^{(i+1)}$ with the ones from the prior iteration using an interpolation weight $\rho$
\begin{equation}
\hat\Theta^{(i)} \leftarrow (1 - \rho) \, \Theta^{(i)} + \rho \, \Theta^{(i-1)} % \quad .
\end{equation}
which leads to an exponentially decreasing impact of the initial parameter set.

>>>>

\subsection{Inter-Iteration Smoothing}
Another typical problem that arises when training semi-continuous models is
that the weights tend to converge to a poor local optimum over the iterations. 
Our intuition is that the weights tend to overfit to the Gaussian parameters
in such a way that the model quickly converges with the
GMM parameters very close to the initialization point.
%
To try to counteract this effect, we smooth the newly estimated parameters 
$\Theta^{(i+1)}$ with the ones from the prior iteration using an interpolation weight $\rho$
\begin{equation}
\hat\Theta^{(i)} \leftarrow (1 - \rho) \, \Theta^{(i)} + \rho \, \Theta^{(i-1)} % \quad .
\end{equation}
which leads to an exponentially decreasing impact of the initial parameter set.
We implemented this for all the parameters but found it only helped when
applied to just the weights,
which is consistent with our interpretation that stopping the weights from overfitting
too fast allows the Gaussian parameters to move farther away from the initialization
than they otherwise would.
We note that other practitioners have also used mechanisms that
prevent the weights from changing too fast and
have found that this improved results\footnote{Jasha Droppo, personal communication.}.
